Using temperature distributions of active regions to investigate flare activity

### 2015-03-11 paper.tex
Minor intro edits

Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download process.
As such this is a preliminary work investigating a relatively small number of flares and the results should not be considered definitive.
Rather they are a proof of concept.
They demonstrate the type of study made available by fast temperature analysis of the corona, which has only become possible. % Perhaps some rephrasing here?

>>>>

Although it is faster than others of its kind, the temperature-calculating method used here requires a very large amount of AIA data, which can take a long time to download and process.
As such this is work investigates only a relatively small number of flares and the results should not be considered definitive.
Rather they are a proof of concept; they demonstrate the type of study made available by fast temperature analysis of the corona, which has only been made possible by the high-quality data provided by AIA.
